### 2016-08-28 Chapters/QuantumMechanics.tex
Work on the summary of papers
Massage the introduction
Work on introduction

% mainfile: ../RobertoDiRemigioPhDThesis.tex
\chapter{A Quick Tour of Molecular Quantum Mechanics}\label{ch:QM}

\begin{itemize}
  \item nonrelativistic and relativistic Hamiltonians use in molecular
    quantum mechanics
  \item Fock space
  \item single-reference methods: \ac{HF} and \ac{KS} \ac{DFT}
\end{itemize}

>>>>

% mainfile: ../RobertoDiRemigioPhDThesis.tex

\renewcommand{\thefigure}{\arabic{chapter}.\arabic{figure}}

\chapter{A Quick Tour of Quantum Chemistry}\label{ch:QM}

\begin{itemize}
  \item nonrelativistic and relativistic Hamiltonians used in molecular
    quantum mechanics
  \item \ac{BO} approximation and the concept of \ac{PES}
  \item Fock space
  \item single-reference methods: \ac{HF} and \ac{KS} \ac{DFT}
\end{itemize}

### 2016-08-28 FrontBackmatter/Introduction.tex
Work on introduction

\begin{figure}[tb]
\centering
\scalebox{0.8}{\input{gfx/RQC-axes.tikz}}
\caption{The three dimensions of Relativistic Quantum Chemistry. The computational scaling of a relativistic model chemistry is
$ S=\textcolor{red}{y}(\textcolor{blue}{x})f(\textcolor{blue}{x})\textcolor{green}{M}^{\textcolor{blue}{x}} $. The expense of relativity is in
the appearance of a new prefactor, not in the $M$-dependence of the particular method.}
\label{fig:RQC-axis}
\end{figure}
and look at different axes.

@@

\todo[inline]{Write something about the scope of molecular quantum
mechanics.}

@@

>>>>

@@

\todo[inline]{Quantum chemistry as they study of
molecular properties by means of \emph{ab initio} physico-mathematical
theories and computer programs.
Introduce the concept of model chemistries, but then mention that we are
interested in different aspects and will look at different "axes".}

@@

\begin{figure}[!h]
\centering
\scalebox{0.8}{\input{gfx/RQC-axes.tikz}}
\caption{
Pictorial depiction of the concept of \emph{model chemistries} as the
three dimensions of quantum chemistry.~\autocite{Pople1999-gt, Saue2011-qg}
The computational scaling of a model chemistry is
$S=\textcolor{PMS1797}{y}(\textcolor{PMS2229}{x})f(\textcolor{PMS2229}{x})\textcolor{PMS130}{M}^{\textcolor{PMS2229}{x}}$.
}
\label{fig:RQC-axis}
\end{figure}
